\documentstyle[12pt,fullpage,steve]{article}
\setcounter{page}{1}

\begin{document}

\title{EE 150.2 Project Demo Checklist}
\author{Total Marks Possible = 25}
\date{}
\maketitle

Correctness:
\begin{enumerate}
\item Can players chooses color (b/w) of playing pieces.
\item Can players decide which player goes first.
\item Does the Move input make sense and correspond to the gameboard.
\item Does the game proceed normally - ie alternate players, alternate colors,
 right color  for right player, etc.
\item Can you call up the rules?  Can you get a (shorter) help menu?
\item Does the game detect  a simple win :
  \begin{itemize}
   \item  5 in a row
   \item 5 in a colum
   \item 5 in a diagonal
  \end{itemize}
\item The board must NOT be square - ie it must be displayed on an angle like
 the "real" game.
\item If Player X runs out of chips does he get to use Player Y's chip for his
 turn ?    
\item Do chips slide out the bottom ok?  
\item Does the chip count work correctly  when slides do or do not happen?
\item When you "slide" spaces should NOT slide - verify.
\item Can you break the game with bad input ?  
\end{enumerate}

** Go To Next Page >>>>
\newpage

Bonus:
\begin{itemize}
\item [A.] Does the automatic player option work?
\item [B.] How does the automatic player work? 
\item [C.] Try a game and see if it works.
\item [D.] Ask if there are any other options or features they would
like to show off.
\end{itemize}

Style to check:
\begin{enumerate}
\item Board looks good.
\item Bad moves not allowed.  
\item Error checking handled nicely.
\end{enumerate}

Questions to be asked to the group. Do the answers make sense, if not why? 
\begin{enumerate}
\item Ask, then check:  What does the game do in the case where both players win?
\item Ask only: Does the game detect a case in which no one wins.  How?
\item Who did what?  Ask a question to each member about how his/her section
 works ?
\item Who merged it all together?  What problems did they have ?  
\end{enumerate}

Comments:
\begin{enumerate}
\item
\vspace{0.1in} 
\item
\vspace{0.1in} 
\item
\vspace{0.1in} 
\item
\vspace{0.1in} 
\item
\end{enumerate}
\end{document}

